Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-02-14 3dpas_intro.tex
refinements up to 5.1.1

The applications in \S\ref{sec:scenarios} show that the dynamic
characteristics of many applications arise in two ways, due to data
generation and placement or due to the coordination
mechanisms of the application.
The first of these refers to data dynamism and the second to
application dynamism (outlined in \S\ref{sec:dynTypes}).

@@

\emph{Data generation, placement and consumption}: In many
applications, data is dynamically generated in response to a user
request or when a particular phenomenon of interest has been
observed. Often this data is large in size and must be placed close to
the user undertaking the analysis. In some instances, it may not be
known where (and when) an analysis request may be made, and it is
therefore necessary to identify how replicas of the data could be
produced and placed across multiple possible locations.  In general,
dynamic data arises due to changing data properties, changing data
volume (generation, consumption, or processing), and changing data
location or distribution.

@@

\emph{Application Dynamism: } In many scientific applications the
workflow structure is well defined, but either the components used
within this structure or the location of the data that feeds the
workflow may change dynamically.  Data coordination and planning
(identifying how data is managed from ingest through analysis to
output) within such applications can range from statically defined
interactions between execution units and data sources to a fully
adaptable interaction using multi-agent systems.  As outlined in the
Industrial Incident Notification and Response application in
(\S\ref{Kees}), the workflow structure may also change based on a user
request or the event being observed. Data relating to the coordination
of a components that make up the application can therefore also be
dynamic and change.  Exposing the data planning used within an
application makes it possible to modify or adapt it over time.

>>>>

The applications in \S\ref{sec:scenarios} show that the dynamic characteristics
of many applications arise in two ways: either due to data generation and
placement, or due to the certain aspects of the application.  The first
of these refers to data dynamism and the second to application dynamism
(outlined in \S\ref{sec:dynTypes}).

@@

\emph{Data generation, placement and consumption}: In many
applications, data is dynamically generated in response to a user
request or when a particular phenomenon of interest has been
observed. Often this data is large in size and must be placed close to
the analysis. In some instances, it may not be
known where (and when) an analysis request may be made, and it is
therefore necessary to identify how replicas of the data could be
produced and placed across multiple possible locations.  In general,
dynamic data arises due to changing data properties, changing data
volume (generation, consumption, or processing), and changing data
location or distribution.

@@

\emph{Application Dynamism: } In many scientific applications the
workflow structure is well defined, but either the components used
within this structure or the location of the data that feeds the
workflow may change dynamically.  Data coordination and planning
(identifying how data is managed from ingest through analysis to
output) within such applications can range from statically defined
interactions between execution units and data sources to a fully
adaptable interaction.  As outlined in the
Industrial Incident Notification and Response application in
(\S\ref{Kees}), the workflow structure may also change based on a user
request or the event being observed. Data relating to the coordination
of a components that make up the application can therefore also be
dynamic and change.  Exposing the data planning used within an
application makes it possible to modify or adapt it over time.
